Analysis for Project

### 2021-11-22 analysis/analysis.Rmd
Add analysis of best way to fit grade-year interaction
I tested multiple models and the best fit was given by a linear year trend interacted with grade. This addresses issue #20.

All models are estimated as logit models. Warning, the code chunks below take a bit of time to run!

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=acs, family=binomial)
model1 <- update(model0, 
                 .~.+as.factor(year)+current_grade+as.factor(state)+metro+sex)
model2 <- update(model1, 
                 .~.+foreign_born+foreign_born_mother+foreign_born_father+
                   spk_eng+spk_eng_mother+spk_eng_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)

>>>>

All models are estimated as logit models.

Before running the full models, I want to test out how I can parsimoniously address differences in the time trends by grade.

```{r}
model_add_cat <- glm(below_exp_grade~as.factor(year)+current_grade, 
                     data=acs, family=binomial)
model_add_cont <- glm(below_exp_grade~I(year-2010)+current_grade, 
                     data=acs, family=binomial)
model_inter_cont <- glm(below_exp_grade~I(year-2010)*current_grade, 
                     data=acs, family=binomial)
model_inter_cat <- glm(below_exp_grade~as.factor(year)*current_grade, 
                     data=acs, family=binomial)

sapply(list("categorical, additive"=model_add_cat,
            "categorical, interaction"=model_inter_cat, 
            "continuous, additive"=model_add_cont, 
            "continuous, interaction"=model_inter_cont), 
       BIC) %>%
    enframe("model","BIC") %>%
  kbl()

# free some memory
rm(model_add_cat, model_add_cont, model_inter_cat, model_inter_cont)
```

The preferred model by BIC is clearly the model that fits year as a continuous measure and interacts it with current grade, so that is what I will do.

Now lets run the full models. Warning, the code chunks below take a bit of time to run!

```{r build-models, results='asis'}
model0 <- glm(below_exp_grade~race, data=acs, family=binomial)
model1 <- update(model0, 
                 .~.+I(year-2010)*current_grade+as.factor(state)+metro+sex)
model2 <- update(model1, 
                 .~.+foreign_born+foreign_born_mother+foreign_born_father+
                   spk_eng+spk_eng_mother+spk_eng_father)
model3 <- update(model2, .~.+degree_mother+degree_father)
model4 <- update(model3, .~.+sqrt(family_income/10000)+own_home+parents_married)
